Death Registrations May Indicate a Discreptency in Reported Data During the COVID-19 Pandemic

### 2023-02-03 outputs/paper/paper.qmd
continue writing

```{r}
#| echo: false
#| warning: false
#| label: fig-1
#| fig-cap: "Death Licenses Provided by All Civic Centres Yearly From 2016-2020 "

@@

When looking at @fig-1, however, we can see that from 2016 to 2018 to there was an increase in death licenses registered, as expected, followed by a slight drop in 2019. This drop in 2019 may be indicative of a backlog from Ontario's Vital Statistics in early 2019 which was cited as having delays of over three months, waiting for death, birth and marriage certificates [@citectvnews]. What is most important in @fig-1 is that when looking at the "2020" bar in @fig-1, we can see that the death licenses registered drops significantly in comparison to any of the previous 4 months.

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "Death Licenses Provided by Month from 2016-2020 at Three Toronto Civic Centres"

>>>>

```{r}
#| echo: false
#| warning: false
#| label: fig-1
#| fig-cap: "Death Licenses Registered at Three Toronto Civic Centres from 2016-2020"

@@

When looking at @fig-1, however, we can see that from 2016 to 2018 to there was an increase in death licenses registered, as expected, followed by a slight drop in 2019. This drop in 2019 may be indicative of a backlog from Ontario's Vital Statistics in early 2019 which was cited as having delays of over three months, waiting for death, birth and marriage certificates [@citectvnews]. What is most important in @fig-1 is that when looking at the "2020" bar in @fig-1, we can see that the death licenses registered drops significantly in comparison to any of the previous 4 months. However, the amount of death licenses registered in 2020 was inconsistent as can be seen in @fig-2.

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "Death Licenses Provided by Month at Three Toronto Civic Centres from 2016-2020"
